---
title: "Data Mining - SVM"
author: "Srushti Padade"
date: "April 14, 2020"
output: html_document
---

#Problem Statement:

Build a Support Vector Machine models. The objective of the support vector machine algorithm is to find a hyperplane in an N-dimensional space that distinctly classifies the data points, here is to predict the type of a breast tumor (benign or malignant).

a)	 Try examine the following values for the C parameter 1,2.5, 6.25
b)	Show the confusion matrix of predictions on the test data (in the above example, I have the raw (class) predictions. You need to compare them with the ground truth values (i.e. testing$Class). 

The library "mlbench" have the BreastCancer Dataset. The inbuild libraries like caret and kernlab are also used for the solution.

```{r}
library(mlbench)
library(caret)
library(kernlab)

options(warn=-1)
```

A data frame with 699 observations on 11 variables, one being a character variable, 9 being ordered or nominal, and 1 target class.

```{r}
data(BreastCancer) 

levels(BreastCancer$Class)
```

The seed is set to 2 and the missing data is manipulated by complete.case(using the na.roughfix() function).
Here we have also converted ID parameter from char to numeric and factorized our target variable for further computation.

```{r}
set.seed(2)

BreastCancer$Class <- as.factor(BreastCancer$Class)
BreastCancer$Id <- as.numeric(BreastCancer$Id)

str(BreastCancer)

#BreastCancer <- na.roughfix(BreastCancer)
BreastCancer <- BreastCancer[complete.cases(BreastCancer),]
```

The dataset is partitioned in 70% Training data and 30% Testing data.

```{r}
intrain <- createDataPartition(y = BreastCancer$Class, p = 0.7, list = FALSE)
training <-BreastCancer[intrain,]

testing <- BreastCancer[-intrain,]

dim(training)
dim(testing)
```

The SVM is executed on the entire training data.
NOTE: Here we have ignored the ID variable for training as it do not specify any important information.

```{r}
svm.model<-train(Class~.,data=training[-1], method='svmLinear')
svm.model
```

The Model developed from the training data is used to predict the outcome of the Testing data where the Tumor Class will be predicted.

```{r}
pred_class_raw <-predict(svm.model, testing[-1],type="raw")

table(pred_class_raw, testing$Class)
```

The above table is a confusion matrix for the prediction where we can see the accuracy of 95.59%.

Similarly, to examine the mtry variable the grid is assigned to 21, 2.5, 6.25 and the SVM is executed again.

```{r}
Grid_Serach <- expand.grid(.C=c(1,2.5,6.25))

svm.model2<-train(Class~.,
                  data=training[-1],
                  method='svmLinear',
                  tuneGrid=Grid_Serach)

svm.model2
```

Again, the Model developed from the training data is used to predict the outcome of the Testing data where the Tumor Class will be predicted.

The raw output is predicted for the testing data and then computed the confusion matrix.

```{r}
pred_class <-predict(svm.model2,testing[-1], type="raw")
head(pred_class)

table(pred_class, testing$Class)
```

We have observed that the accuracy of the testing data is 95.59 %.